A systematic measurement on starspot contrast from TESS and K2 bandpass differences

### 2022-06-20 papers/paper1/ms.tex
Demo writing and start of real content to the paper
Cowriting the outline for the paper

@@

\usepackage[caption=false]{subfig}
\usepackage{booktabs}

@@

\newpage

>>>>

%\turnoffedit

@@

\usepackage[caption=false]{subfig}
\usepackage{censor}
\usepackage{booktabs}

@@

\section{Observations and Data Reduction}

All sources were observed by both the K2 \citep{howell14} and TESS \citep{2015JATIS...1a4003R} missions.

\subsection{Sample selection}
Our initial sample mirrors...
Hello!

\subsection{TESS pipelines}

\subsection{Quality assurance checks}

\subsubsection{Handling data gaps}

\subsubsection{Handling multiple sectors}

\subsubsection{Quality flags}

\subsubsection{Outlier detection}

\authorcomment1{Outliers attributable to instrumental artifacts}.

\authorcomment1{Outliers attributable to flares}.

\authorcomment2{Outliers attributable to exoplanets}.

\section{Analysis}

\subsection{Period measurement}

\subsubsection{Amplitude measurements}

\section{Results}

\subsection{Amplitude versus rotation period for bins in $T_{\mathrm{eff}}$}

\subsection{TESS-to-K2 amplitude ratio as a function of $T_{\mathrm{eff}}$}

\subsection{Converting amplitude ratio to $T_{\mathrm{spot}}$}

\subsection{Inferred $T_{\mathrm{spot}}$ versus $T_{\mathrm{eff}}$}

\section{Discussion}

\subsection{Comparison to other studies}
\citet{2016MNRAS.463.2494F} targeted 304 Pleiades sources with LAMOST and found the $T_{\mathrm{spot}}$ scales with $T_{\mathrm{eff}}$ with figure.

\subsection{Assessing the spots versus faculae}
Up to the this point, we have assumed that all flux variations arise from dark spots on the surface of the star. Stars can just as likely have bright patches that cause flux perturbations to their light curves. Here we assess the consequences of assuming faculae instead of spots.

\section{Conclusions}
